---
title: "p8105_hw5_stl2137"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
```

```{r}
set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```

```{r}
fill_iris <- function(x) {
  if(is.character(x)) {
    replace(x, is.na(x), "virginica")
  } else if(is.numeric(x)) {
    replace(x, is.na(x), mean(x, na.rm = TRUE))
  }
}

filled_iris <- map_df(.x = iris_with_missing, ~fill_iris(.x))
```

## Problem 2

```{r}
long_study_tidy <- list.files(path = "./data/", pattern = "*.csv", full.names = TRUE) %>% 
  map_df(~read_csv(.)) %>% 
  mutate(
    subject_id = list.files("./data") %>% str_extract('.*(?=\\.csv$)')
  ) %>% 
  separate(subject_id, into = c("arm", "subject_number_id"), sep = "_") %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    names_prefix = "week_",
    values_to = "observation"
  ) %>% 
  mutate(
    observation = as.numeric(observation)
  ) 
```

* The experimental group over the 8 weeks have a trend of increasing observations compared with the control group observations over the 8 weeks. 

```{r}
long_study_tidy %>% 
  group_by(arm, subject_number_id) %>% 
  ggplot(aes(x = week, y = observation, group = arm, color = arm)) +
  geom_path() 
```


## Problem 3

In this problem, you will conduct a simulation to explore power in a simple linear regression.

First set the following design elements:

Fix n=30

Fix xi1 as draws from a standard Normal distribution

Fix β0=2

Fix σ2=50

Set β1=0. Generate 10000 datasets from the model yi=β0+β1xi1+ϵi with ϵi∼N[0,σ2]. 

For each dataset, save β̂ 1 and the p-value arising from a test of H:β1=0 using α=0.05. Hint: to obtain the estimate and p-value, use broom::tidy to clean the output of lm.

```{r}

sim_regression = function(n, beta0 = 2, beta1 = 0) {
  
  sim_data = tibble(
    x = rnorm(30, mean = 0, sd = 1),
    y = 2 + beta1 * x + rnorm(30, 0, 50)
  )
  
  ls_fit = lm(y ~ x, data = sim_data)
  
  tibble(
    term = broom::tidy(ls_fit)$term,
    beta1_hat = broom::tidy(ls_fit)$estimate,
    p_value = broom::tidy(ls_fit)$p.value
  )
}

sim_regression(30, 2, 0)

sim_results_0 <- 
  rerun(1000, sim_regression(30, 2, 0)) %>% 
  bind_rows()
```

### REMEMBER TO CHANGE BACK TO 10000 B/C IT TAKES TOO LONG TO RUN ### 

```{r}

output = vector("list", length = 6)

for (i in 1:6) {
  
  output[[i]] = rerun(1000, sim_regression(30, 2, i)) %>% 
    bind_rows()
  
}

sim_results_1_6 <-
  output %>% 
  bind_rows()
```


