---
title: "p8105_hw5_stl2137"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
```

```{r}
set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```


There are two cases to address:

For numeric variables, you should fill in missing values with the mean of non-missing values

For character variables, you should fill in missing values with "virginica"

Write a function that takes a vector as an argument; replaces missing values using the rules defined above; and returns the resulting vector. Apply this function to the columns of iris_with_missing using a map statement

## How would I do this without using a function?
```{r}
sepal_mean_no_na <- iris_with_missing %>% 
  summarise(mean(Sepal.Length, na.rm = TRUE))

iris_with_missing %>% 
  replace_na()
```


```{r}
fill_iris <- function(x) {
  
}

```

## Problem 2
```{r}
long_study_total_list <- list.files(path = "./data")



df <- list(
  control_1 = "con_01.csv",
  control_2 = "con_02.csv",
  control_3 = "con_03.csv",
  control_4 = "con_04.csv",
  control_5 = "con_05.csv",
  control_6 = "con_06.csv"
)

output <- map(df)
```

